\documentclass{article}

\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\usepackage{fontawesome}

\pagenumbering{gobble}

\newcommand\phone{(513) 680-0072}
\newcommand\email{hello@raymondkneipp.com}

% Do not include 'https://'
\newcommand\website{raymondkneipp.com}
\newcommand\linkedinUsername{raymondkneipp}
\newcommand\location{Cincinnati, Ohio}
\newcommand\githubUsername{raymondkneipp}

\begin{document}


	\begin{center}
		{\Huge Raymond Kneipp}

		\vspace{5 mm}

		\begin{tabular}{ l l l }
			\faGithub \ \href{https://github.com/\githubUsername}{github.com/\githubUsername} & \faLinkedinSquare \ \href{https://linkedin.com/in/\linkedinUsername}{linkedin.com/in/\linkedinUsername} & \faGlobe \ \href{https://\website}{\website} \\
			\faEnvelope \ \href{mailto:\email}{\email} & \faPhone \ \href{tel:\phone}{\phone} & \faMapMarker \ \location \\
		\end{tabular}
	\end{center}

	\section*{Work Experience}
	
	\subsection*{Full Stack Web Developer - \url{https://alpost.org}}

	May 2022 - Present
	
	\begin{itemize}
		\item Developed website builder for American Legion Posts using a multi-tenant architecture with the Next.js framework.
		\item Constructed a content management system to control site data, edit website content, and manage legion members through a custom-built admin dashboard.
		\item Crafted React UI component library to use throughout the app enabling rapid development of new features.
		\item Implemented and managed subscription payments, utilizing Stripe.js to process transactions and secure credit card information.
	\end{itemize}

	\subsection*{Web Developer - \url{https://alssweeper.vercel.app/}}

	January 2021 - Present
	
	\begin{itemize}
		\item Converted designs into reusable React components and developed site layout, implementing SEO best practices.
		\item Implemented static generation decreasing load time by over 40\%, increasing site efficiency and page speed.
		\item Developed an e-commerce solution using the commerce.js library to create an intuitive and seamless shopping experience for customers.
		\item Utilized Redux Toolkit to manage and store data pertaining to the shopping cart.
	\end{itemize}

	\subsection*{Web Developer - \url{https://eaachapter174.vercel.app/}}

	May 2019 - Present
	
	\begin{itemize}
		\item Designed and developed a website with all required content, coding, and uploading media, including newsletters on behalf of client in order to produce a fully operational site.
		\item Revamped legacy website into an easy-to-use mobile-friendly platform while adhering to Search Engine Optimization (SEO) best practices.
		\item Increased online engagement by more than 11\% within first six months.
	\end{itemize}

	\subsection*{Communications Engineer - Marine Corps Reserve}

	October 2018 - Present
	
	\begin{itemize}
		\item Awarded The Navy and Marine Corps Achievement Medal after diagnosing and repairing two generators valued at over 53,000 dollars preventing any interruption to the detachment's communications mission.
		\item Tested cables using volt-OHM meters and spectrum analyzers enabling over 1,800 hours of connectivity.
		\item Awarded Gator of the Month for work ethic during the establishment of DJC2.
		\item Provided training on equipment use, troubleshooting, and calibration.
		\item Connected components to external cable systems according to schematics and tested connections for adequate power and functional links.
	\end{itemize}

	\section*{Skills}
	
	HTML, CSS, JavaScript, TypeScript, Git / GitHub, React.js, Next.js, Prisma, tRPC, Tailwind CSS, MongoDB, Express.js, Node.js, MySQL
	
\end{document}